SunPy - Python for Solar Physics

### 2014-08-26 4-Util.tex
Fixed issue #70
typo fix

\section{Additional functionality}\label{sec:util}
SunPy is meant to provide a consistent environment for solar data analysis. In 
order to achieve this goal SunPy provides a number of additional functions and packages which 
are used by the other SunPy modules and are made available to the user. This section 
briefly describes some of these functions.

@@

The \texttt{sunpy.sun.constants} module provides a number of solar-related 
constants in order to enable the calculation of derived solar 
values within SunPy, but also to the user. All solar 
constant are provided as \texttt{Constant} objects as defined in the Astropy \texttt{units} package. Each 
\texttt{Constant} object defines a \texttt{Quantity}, along with 
the constant's provenance (i.e., reference) and its uncertainty. The use of this package
is shown in Listing~\ref{code:constants_code}.
For convenience, a number of shortcuts to frequently used constants are provided 
directly when importing the module. A larger list of constants can be 
accessed through an interface modeled on that provided by the SciPy \texttt{constants}
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly, a \texttt{print\_all()} function is available.

>>>>

\section{Additional Functionality}\label{sec:util}
SunPy is meant to provide a consistent environment for solar data analysis. In 
order to achieve this goal SunPy provides a number of additional functions and packages which 
are used by the other SunPy modules and are made available to the user. This section 
briefly describes some of these functions.

@@

The \texttt{sunpy.sun.constants} module provides a number of solar-related 
constants in order to enable the calculation of derived solar 
values within SunPy, but also to the user. All solar 
constants are provided as \texttt{Constant} objects as defined in the Astropy \texttt{units} package. Each 
\texttt{Constant} object defines a \texttt{Quantity}, along with 
the constant's provenance (i.e., reference) and its uncertainty. The use of this package
is shown in Listing~\ref{code:constants_code}.
For convenience, a number of shortcuts to frequently used constants are provided 
directly when importing the module. A larger list of constants can be 
accessed through an interface modeled on that provided by the SciPy \texttt{constants}
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly, a \texttt{print\_all()} function is available.
